Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
update abstract

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify MCs and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to 
those observed in starburst galaxies.
The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC found in the arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}\approx$2 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
Next Generation Very Large Array (ngVLA)
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

The growth of galaxies and their subsequent evolution are governed by the baryon cycle ---
galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes)
and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
The general consensus is that the growth of \highz galaxies are triggered and supported by massive
gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves 
are more gas-rich in their star-forming molecular
gas contents compared to present-day galaxies.
% while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when
% the gravitational potential is still increasing), but their gas reservoirs
% are continuously being replenished.
These massive gas inflows in turn trigger gravitational instability and lead
to the formation of gas structures that are typically more massive and denser than those
observed in nearby galaxies, with masses of $M_{\rm cl}$\eq10$^9$\,\Msun
and sizes on sub-kpc scales (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
Some theoretical works argue that the
migration of such giant massive clumps are responsible for contributing to the
buildup of the bulges of massive galaxies at \z$\sim$0 \citep[e.g.,][]{Ceverino10a}.

Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies 
since the cosmic dark ages.
Current consensus is that at higher redshifts, galaxies have higher 
star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and 
smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to those found in the local Universe.
The former are thus expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks. 
Since their metallicity and dust content are also expected to be lower as they are assembling, 
this affects the shielding of UV photons, heating and cooling mechanisms in these early systems. Such differences in turn 
affect the regulation of thermal and chemical structures of their ISM. 
Their multi-phase ISM and the dynamics of the star-forming molecular cloud complexes (MC)
are therefore expected to differ from nearby galaxies.
Even in the local Universe, where the most detailed \obs can be attained, variations in cloud properties have been 
observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
It is thus intuitive and reasonable to pose the question: what are the dynamical states of the MCs of the first galaxies and 
how do they differ from the local Universe, and are they analogous to any seen in the local \galpop?
%

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, spatially resolved ISM properties of \highz galaxies
have only been examine observationally in a handful of (strongly-lensed)
galaxies, using tracers such as
dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that galaxies at $z$\ssim2 galaxies, close to the peak of cosmic \SF, are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
That said, it remains unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 --- 
the epoch of reionization  ---
which is responsible for producing the
ionizing photons that reionized the Universe.

While ALMA has enabled the detections of
ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission inr
normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Odorico18a, Carniani18b},
we are still far from mapping their molecular ISM due to the cosmological dimming.
As such, we have undertaken a study, exploiting
state-of-the-art cosmological zoom-in hydrodynamic simulation
\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), to examine
the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$) 
galaxy.

This paper is structured as follows.
\AP{TBM}
In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower),
and describe the method used to identify its molecular gas complexes (MC).
In \Sec{results}, we present scaling relations based on
the MC identified and compare them with observations of molecular
(sub-)structures seen in nearby and \z$>$\,0 galaxies.
We present Toomre stability analysis in \Sec{Q} and
the cumulative mass distribution of the MCs in \flower in \Sec{cmf}.
In \Sec{diss}, we discuss the results and implications of our findings,
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/CMF_.png}
\caption{
CMF of MCs in \flower and best-fit power law.
\label{fig:cmf}}
\end{figure*}

@@

% a bit on caveat
One should, however, keep in mind that 
the slope of the CMF reported here is subject
to the uncertainties in the analysis method and the resolution of our simulation. 
That is, we are likely biased to finding more massive clouds due to resolution effects; 
it is possible that we may identify more less massive MCs if our simulation 
was done at a higher resolution. 
That said, one must acknowledge that such a zoom-in simulation is currently quite expensive to perform with 
existing computational power.
In any case, similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy 
simulations done at higher resolution (e.g., \citealt{Behrendt16a}). 
Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations 
since they adopt non-cosmological initial conditions. 
It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
Future higher resolution zoom-in simulations would certainly be useful to understand
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
% 
%On the contrary, an advantage of using cosmological zoom-in simulations for this study
%is that our computational boxes are not closed, allowing us to examine how
%the molecular complexes' properties vary under the influence of gas inflow/outflow 
%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas

@@

The high pressure observed in \flower is also comparable to what has been observed in local ULIRGs; however, the 
molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70$-$100\,pc and masses on the order of $\sim$10$^9$\,\Msun
\citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are 
found throughout the disk. This difference likely stems from the different physical mechanisms giving rise 
to the formation (and thus the nature) of these molecular structures. 
For instance, in local ULIRGs, they are probably form by shock compression or cloud-cloud 
collision after the large amount of gas from the progenitor galaxy merger 
is being funneled toward the central region \citep{Tan00a, Wu18a},  % Tasker09a
whereas in \flower, which is actively accreting gaseous materials 
from the surrounding, they are probably form from constant cold gas accretion onto the entire galaxy (without 
requiring gas to be funneled into the central region).
This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed 
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{}).
The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render 
the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which would be consistent with/explain the 
high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.

@@

We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in $z$\ssim2 starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
This is consistent with what has been found previously in higher resolution simulation of isolated galaxies \citep{}.
That said, our cosmological zoom-in simulation here allows us to examine 
the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).

@@

\appendix
\section{Schmidt-Kennicutt Relation}
As benchmarking, we check the SK relation for the MCs identified based on their SFR and gas surface densities.
We show in \Fig{sk} the MCs of \flower, identified using different $n_{\rm cut}$ in the ``accreting snapshot'' 
(see \Sec{sfh} for details) compared to those reported in \obs.

\AP{i m currently a bit confused on how to re-generate pickle files to be used for the plot}
\DL{by running test\_brute.py}

\AP{I would put a figure with the SK-relation for the clumps in a single snapshot for different cuts, along with the observed points and the global \flower point from the data found in \citet{Pallottini17a}}
\DL{to do... after getting points from Pallo, then update plot\_cloud\_prop.py and plotsingleSS.py (uncomment plot\_suff(SK) and only plot snapshot 16)}

\begin{figure*}[htbp]
\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/CMF_.png}
\caption{
\AP{figure not found in the path}
SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
\citealt{Pallottini17b}.
%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
%and references therein, and Sharon et al. in prep.
\label{fig:sk}}
\end{figure*}

>>>>

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify MCs and their sub-structures.
We extract properties such as mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) 
for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to 
those observed in starburst galaxies.
The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MCs found in the main disk of \flower are unbound, but its substructures have lower virial parameters. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback 
due to the less frequency \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the former).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the intergalactic medium.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are insensitive to the choice of $n_{\rm cut}$, except for the slope of the cumulative 
mass distribution, which steepens with $n_{\rm cut}$. 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
Next Generation Very Large Array (ngVLA)
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

The growth of galaxies and their subsequent evolution are governed by the baryon cycle ---
galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes)
and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
The general consensus is that the growth of \highz galaxies are triggered and supported by massive
gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves 
are more gas-rich in their star-forming molecular
gas contents compared to present-day galaxies.
% while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when
% the gravitational potential is still increasing), but their gas reservoirs
% are continuously being replenished.
These massive gas inflows in turn trigger gravitational instability and lead
to the formation of gas structures that are typically more massive and denser than those
observed in nearby galaxies, with masses of $M_{\rm cl}$\eq10$^9$\,\Msun
and sizes on sub-kpc scales (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
Some theoretical works argue that the
migration of such giant massive clumps are responsible for contributing to the
buildup of the bulges of massive galaxies at \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these relatively more extreme conditions, thereby driving the evolution and assembly 
of galaxies 
since the cosmic dark ages.
Current consensus is that at higher redshifts, galaxies have higher 
star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and 
smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to those found in the local Universe.
The former are thus expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks. 
Since their metallicity and dust content are also expected to be lower as they are assembling, 
this affects the shielding of UV photons, heating and cooling mechanisms in these early systems. Such differences in turn 
affect the regulation of thermal and chemical structures of their ISM. 
Their multi-phase ISM and the dynamics of the star-forming molecular cloud complexes (MC)
are therefore expected to differ from nearby galaxies.
Even in the local Universe, where the most detailed \obs can be attained, variations in cloud properties have been 
observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
It is thus intuitive and reasonable to pose the question: what are the dynamical states of the MCs of the first galaxies and 
how do they differ from the local Universe, and are they analogous to any seen in the local \galpop?
%

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is necessary to understand their roles in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, spatially resolved ISM properties of \highz galaxies
have only been examine observationally in a handful of (strongly-lensed)
galaxies, using tracers such as
dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that galaxies at $z$\ssim2 galaxies, close to the peak of cosmic \SF, are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
That said, it remains unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 --- 
the epoch of reionization  ---
which is responsible for producing the
ionizing photons that reionized the Universe.

While ALMA has enabled the detections of
ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission in
normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Odorico18a, Carniani18b},
we are still far from mapping their molecular ISM due to the cosmological dimming.
As such, we have undertaken a study, exploiting
state-of-the-art cosmological zoom-in hydrodynamic simulation
\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), to examine
the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$) 
galaxy.

This paper is structured as follows.
\AP{TBM}
In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
and describe the method used to identify its molecular gas complexes.
In \Sec{results}, we present scaling relations based on
the MC identified and compare them with observations of molecular
(sub-)structures seen in nearby and \z$>$\,0 galaxies.
We present Toomre stability analysis in \Sec{Q} and
the cumulative mass distribution of the MCs in \flower in \Sec{cmf}.
In \Sec{diss}, we discuss the results and implications of our findings,
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/CMF_.png}
\caption{
CMF of MCs in \flower and best-fit power law.
\label{fig:cmf}}
\end{figure}

@@

% a bit on caveat
One should, however, keep in mind that 
the slope of the CMF reported here is subject
to the uncertainties in the analysis method and the resolution of our simulation. 
That is, we are likely biased to finding more massive clouds due to resolution effects; 
it is possible that we may identify more less massive MCs if our simulation 
was done at a higher resolution. 
That said, one must acknowledge that such a zoom-in simulation is currently quite expensive to perform with 
existing computational power.
In any case, similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy 
simulations done at higher resolution (e.g., \citealt{Behrendt16a}). 
Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations 
since they adopt non-cosmological initial conditions. 
It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$\,30\,pc).
Future higher resolution zoom-in simulations would certainly be useful to understand
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
% 
%On the contrary, an advantage of using cosmological zoom-in simulations for this study
%is that our computational boxes are not closed, allowing us to examine how
%the molecular complexes' properties vary under the influence of gas inflow/outflow 
%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas

@@

The high pressure observed in \flower is also comparable to what has been observed in local ULIRGs; however, the 
molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70$-$100\,pc and masses on the order of $\sim$10$^9$\,\Msun
\citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are 
found throughout the disk. This difference likely stems from the different physical mechanisms giving rise 
to the formation (and thus the nature) of these molecular structures. 
For instance, in local ULIRGs, they are probably form by shock compression or cloud-cloud 
collision after the large amount of gas from the progenitor galaxy merger 
is being funneled toward the central region \citep{Tan00a, Wu18a},  % Tasker09a
whereas in \flower, which is actively accreting gaseous materials 
from the surrounding, they are probably form from constant cold gas accretion onto the entire galaxy (without 
requiring gas to be funneled into the central region).
This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed 
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}).
The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render 
the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which would be consistent with/explain the 
high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.

@@

We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in $z$\ssim2 starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
This is consistent with what has been found previously in higher resolution idealized simulation of isolated galaxies.
That said, our cosmological zoom-in simulation here allows us to examine 
the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).

@@

\appendix
\section{Schmidt-Kennicutt Relation}
As benchmarking, we check the SK relation for the MCs identified based on their SFR and gas surface densities.
We show in \Fig{sk} the MCs of \flower identified in the accreting phase using different $n_{\rm cut}$
(see \Sec{sfh} for details) and those reported in nearby and \highz \obs \citep{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a}.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
\caption{
SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
\citealt{Pallottini17b}.
%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
%and references therein, and Sharon et al. in prep.
\label{fig:sk}}
\end{figure*}
